Long name of the paper

### 2018-10-23 anzjs2018/sections/04_implementation.tex
some words

The simulations we discuss here use a subset of real data from 8~October, 2018.
This allows us to run the model with different parameters over the same data.
The parameters varied were the number of particles,
GPS error $\epsilon^2$, and system noise $\sigma^2$.
The primary goal is to reduce the rate of degeneration and ``losing'' the bus 
(i.e., no particles are near the observed location),
and reducing the variance of parameter estimates; here we use vehicle speed as the example.

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.7\textwidth]{figures/04_model_results_timing.pdf}
    \caption{The timings for various parts of the application, and overall. %
        The trend is approximately linear with the number of particles.}
    \label{fig:figure1}
\end{figure}

@@

To check the model results, 
we need to realise that we are not trying to accurately predict
future locations of the vehicle,
but instead are trying to use a sequence of GPS positions to infer travel
times along intermediate roads.
Therefore, several tools used to assess the validity of a particle filter
are unnecessary.
Instead, we will be comparing the rate of degeneration 
(i.e., the particle sample loses the actual bus and needs to be reinitialized)
and the mean distance between the state estimate and the observation.
[We also explore the uncertainty of travel time estimates,
as well as the variability between consecutive buses]\footnote{assuming we can get the results in time}.

>>>>

The simulations we discuss here use a subset of real data from 8~October, 2018.
This allows us to run the model with different parameters over the same data.
The parameters varied were the number of particles and system noise $\sigma^2$.
The primary goal is to reduce the rate of degeneration and ``losing'' the bus 
(i.e., no particles are near the observed location),
and reducing the variance of parameter estimates; here we use vehicle speed as the example.

The one parameter we can determine from the data is GPS error, $\epsilon^2$,
by looking at the distance between observations and the shape.
Figure~\ref{fig:gps_dist} shows the distribution of distance between the vehicle
observation and the \emph{nearest point on the path}.
Due to the way the observations are reported, 
many observations will be ``exactly'' on the route at a bus stop,
and we need to ignore these.

\begin{figure}[tb]
    \centering
    % \includegraphics[width=0.7\textwidth]{figures/04_model_results_gps.pdf}
    \caption{The distance between the observation and the nearest point on the shape.}
    \label{fig:gps_dist}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.7\textwidth]{figures/04_model_results_timing.pdf}
    \caption{The timings for various parts of the application, and overall. %
        The trend is approximately linear with the number of particles.}
    \label{fig:timings}
\end{figure}

@@

To check the model results, 
we need to realise that we are not trying to accurately predict
future locations of the vehicle,
but instead are trying to use a sequence of GPS positions to infer travel
times along intermediate roads.
Therefore, several tools used to assess the validity of a particle filter
are unnecessary.
Instead, we will be comparing the rate of degeneration 
(i.e., the particle sample loses the actual bus and needs to be reinitialized)
and the mean distance between the state estimate and the observation,
[We also explore the uncertainty of travel time estimates,
as well as the variability between consecutive buses]\footnote{assuming we can get the results in time}.
